---
title: "SIS Completion Summary"
output: pdf_document
classoption: landscape
params:
  summary_tbl: summary
  report_date: Sys.Date()
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE)
library(tidyverse)
```

# Completion by CMHSP

```{r tbl_output}
knitr::kable(
  params$summary_tbl,
  col.names = c(
    "Organization","Denom.","Denom. FY","Num.","Eligible","Due FY",
    "Compl. (E)","Compl. (I)","Overdue","Deferred","% Complete","% FY"
  ),
  format.args = list(big.mark = ',')
)
```

# Definitions

The following definitions relate to the columns of the table above:

- **Organization:**  *Name of the organization.*  For CMHSPs, this is the name of the organization who most recently submitted claims for any service provided to an individual.
- **Denom:** *Denominator: Individuals who were eligible for or received a SIS.*  The number of individuals who are eligible to receive a Supports Intensity Scale (SIS) assessment and who have not deferred participation in the assessment.  The denominator does *not* include *Completed (I)* assessments for individuals who were not flagged as eligible but who nevertheless received an assessment. 
- **Denom. FY:** *Denominator for Current FY: Individuals who are eligible for or received a SIS during the current FY.*  The number of individuals who are eligible to receive a Supports Intensity Scale (SIS) assessment which is *Due in FY* and who have not refused to participate in the assessment.  The denominator does *not* include *Completed (I)* assessments for individuals who were not flagged as eligible but who nevertheless received an assessment.
- **Num.:** *Numerator: Individuals with a current SIS.*  The number of individuals who have received a SIS assessment within the past three years.  The numerator is determined by looking at the total number of *Compl. (E)* assessments and subtracting those which are *Overdue*.  
- **Eligible:**  *Individuals eligible to receive a SIS*  The total number of individuals who were eligible to receive a SIS assessment based on the following criteria: (a) 18 years or older, (b) have an intellectual or developmental disability, (c) have Medicaid/Healthy MI Medicaid, and (d) receiving case management, supports coordination, respite, home-based, or ACT services.
- **Due FY:**  *Individuals with SIS due within current FY.*  This is the number of individuals with a SIS assessment due during the current fiscal year (i.e. before 9/30 of the fiscal year on which the report was run).  
- **Compl. (E):**  *Eligible individuals with a completed SIS.*  The total distinct number of *Eligible* individuals who have had a SIS assessment completed at any time, based on the SIS Online extract.
- **Compl. (I):**  *Ineligible individuals with a completed SIS.*  The total distinct number of individuals who have had a SIS assessment completed at any time, based on the SIS Online extract, but who were not identified as *Eligible*.
- **Overdue:**  *Individuals with an expired SIS.*  The number of individuals with a *Completed* SIS (whether eligible or ineligible) whose assessment occurred more than three years prior to the date of this report.
- **Deferred:** *Individuals who refused to take SIS.*  The number of individuals who opted not to participate in a SIS assessment.  Since deferrals are considered active for a year, after which time it is expected that follow-up will occur, this count only includes 'active' deferrals which were made within one year prior to the report date.
- **% Complete:** *Individuals with a current SIS / Individuals eligible for SIS.*  The percent completed is determined by taking the number of individuals who received or were eligible to receive a SIS assessment who did not refuse to receive the assessment (*Denominator*), and looking at the proportion of these individuals who have a current SIS (i.e. within the past 3 years) based on assessment data (*Numerator*).
- **% FY:** *Individuals with a current SIS / Individuals who were eligible for or received a SIS during the FY.*  The percent completed is determined by taking the number of individuals who received or were eligible to receive a SIS assessment who did not refuse to receive the assessment (*Denom. FY*), and looking at the proportion of these individuals who have a current SIS (i.e. within the past 3 years) based on assessment data (*Numerator*).  Note that this number can be greater than 100% if more assessments have been completed than those required during the FY.
   
# Data

This report was generated on `r params$report_date`.


