---
title: "SIS Completion Summary"
output: pdf_document
params:
  summary_tbl: summary
  report_date: Sys.Date()
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE)
library(tidyverse)
```

# Completion by CMHSP

```{r tbl_output}
knitr::kable(
  params$summary_tbl,
  col.names = c("Organization","Denominator","Numerator","Completed","Overdue","Deferred","% Complete"),
  format.args = list(big.mark = ',')
)
```

# Definitions

The following definitions relate to the columns of the table above:

- **Organization:**  *Name of the organization.*  For CMHSPs, this is the name of the organization who most recently submitted claims for any service provided to an individual.
- **Denominator:** *Individuals eligible for SIS.*  The number of individuals who are eligible to receive a Supports Intensity Scale (SIS) assessment and who have not refused to participate in the assessment.  Note that the total number of eligible individuals can be calculated by adding the *Denominator* and *Deferred* fields
- **Numerator:** *Individuals with a current SIS.*  The number of individuals who have received a SIS assessment within the past three years.  The numerator is determined by looking at the total number of assessments *Completed* and subtracting those which are *Overdue*.  Note that because the numerator may include individuals who do not meet eligibility criteria, it is possible for the *Numerator* to be greater than the *Denominator*.
- **Completed:**  *Individuals with a completed SIS.*  The total distinct number of individuals who have had a SIS assessment completed at any time, based on the SIS Online extract.
- **Overdue:**  *Individuals with an expired SIS.*  The number of individuals with a *Completed* SIS whose assessment occurred more than three years prior to the date of this report.
- **Deferred:** *Individuals who refused to take SIS.*  The number of individuals who opted not to participate in a SIS assessment.
- **% Complete:** *Individuals with a current SIS / Individuals eligible for SIS.*  The percent completed is determined by taking the number of individuals eligible to receive a SIS assessment who did not refuse to receive the assessment (*Denominator*), and looking at the proportion of these individuals who have a current SIS (i.e. within the past 3 years) based on assessment data (*Numerator*).
   
# Data

This report was generated on `r params$report_date`.


