---
title: 'SIS Completion: Directors Summary'
author: "Region 10"
output: pdf_document
params:
  summary_tbl: summary
  report_date: Sys.Date()
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE)
library(tidyverse)
```

# Completion by CMHSP

```{r tbl_output}
params$summary_tbl %>%
  select(
    CMHSP,
    `Individuals eligible or received SIS (Denominator)`,
    `Individuals with a current SIS (Numerator)`,
    `Individuals eligible to receive SIS`,
    `Individuals with a current SIS / Individuals eligible for SIS`,
    `Individuals with SIS due in current Fiscal Year`
  ) %>%
  knitr::kable(
    col.names = c("Organization","Denominator","Numerator","Eligible","% Complete","Due this FY"),
    format.args = list(big.mark = ',')
  ) 
```

# Definitions

The following definitions relate to the columns of the table above:

- **Organization:**  *Name of the organization.*  For CMHSPs, this is the name of the organization who most recently submitted claims for any service provided to an individual.
- **Denominator:** *Individuals who were eligible for or received a SIS.*  The number of individuals who are eligible to receive a Supports Intensity Scale (SIS) assessment and who have not deferred participation in the assessment.  The denominator does *not* include *Completed (I)* assessments for individuals who were not flagged as eligible but who nevertheless received an assessment. 
- **Numerator:** *Individuals with a current SIS.*  The number of individuals who have received a SIS assessment within the past three years.  The numerator is determined by looking at the total number of *Compl. (E)* assessments and subtracting those which are *Overdue*.
- **Eligible:**  *Individuals eligible to receive a SIS*  The total number of individuals who were eligible to receive a SIS assessment based on the following criteria: (a) 18 years or older, (b) have an intellectual or developmental disability, (c) have Medicaid/Healthy MI Medicaid, and (d) receiving case management, supports coordination, respite, home-based, or ACT services.
- **% Complete:** *Individuals with a current SIS / Individuals eligible for SIS.*  The percent completed is determined by taking the number of individuals who received or were eligible to receive a SIS assessment who did not refuse to receive the assessment (*Denominator*), and looking at the proportion of these individuals who have a current SIS (i.e. within the past 3 years) based on assessment data (*Numerator*).
- **Due this FY:**  *Individuals with SIS due within current FY.*  This is the number of individuals with a SIS assessment due during the current fiscal year (i.e. before 9/30 of the fiscal year on which the report was run).  Note that this number includes individuals who may fall out of the numerator during the remainder of the year due to the expiration of their SIS assessment.
   
# Data

This report was generated on `r params$report_date`.
