---
title: "Missing BH-TEDS records?"
output: html_notebook
---

What is the cause of the missing (NA) admission dates?

We start the process of identifying eligible individuals with service data, which we have going back to `r min(svs$FROM_DATE)`.  We left-join this to the admission date from BH-TEDS, so it follows that missing admission dates will be due to one of two reasons: (a) the `agency_admission_date` field is blank in the BH-TEDS data, or (b) there is no `medicaid_id` field to join to in the BH-TEDS data.

If we keep only the most recent BH-TEDS file for each `case_#`, there are `r sum(is.na(open_date$medicaid_id))` BH-TEDS records in the data submitted which are missing a `medicaid_id`.  I've spot-checked the original Excel output reports and the ones I checked are indeed blank in those files.

There are only `r sum(is.na(open_date$agency_admission_date))` BH-TEDS records in the data submitted which are missing an `agency_admission_date`, so this doesn't seem to be the issue.

We can pull a list of Medicaid IDs which are present in the services data but not in the BH-TEDS files like so:

```{r in_svs_not_teds}
in_svs_not_teds <- setdiff(unique(svs$MEDICAID_ID),unique(open_date$medicaid_id))
```

There are `r length(in_svs_not_teds)` IDs that are in the services data but not BH-TEDs files that I received.  Of course, not all individuals receiving services are eligible to receive a SIS.  

```{r in_siselig_not_teds}
in_siselig_not_teds <- setdiff(unique(need_sis$MEDICAID_ID),unique(open_date$medicaid_id))
```

If we look only at beneficiaries from who are eligible for the SIS (which I believe Laurie was referring to as the 'sample'), we find `r length(in_siselig_not_teds)` IDs that are in the SIS eligible population but not BH-TEDs files that I received.

There is service data for at least some of these individuals going back to `r svs %>% filter(MEDICAID_ID %in% in_siselig_not_teds) %>% summarize(min_svc_dt = min(FROM_DATE)) %>% .$min_svc_dt` and as recent as `r svs %>% filter(MEDICAID_ID %in% in_siselig_not_teds) %>% summarize(max_svc_dt = max(FROM_DATE)) %>% .$max_svc_dt`, so this doesn't seem like an issue where the person has not had time for a BH-TEDS record to be completed, or where they received services before BH-TEDS was a requirement.


Possible reasons:

- A BH-TEDS file was not completed
- The BH-TEDS file does not contain a Medicaid ID
- The Medicaid ID field in the BH-TEDS file does not match the Medicaid ID on the service (i.e. one of them is entered incorrectly)

If you could spot check some of the IDs that are in the SIS eligible population but not BH-TEDs files that I received by looking in the MIX system, that would be wonderful.  Here's the list:

`r in_siselig_not_teds`
